---
title: "cavega_OriginalHomeworkCode_02"
author: "C. Vega"
date: "9/16/2019"
output: html_document
---

# This is the code for [Homework 2](https://fuzzyatelin.github.io/bioanth-stats/homework-02.html)
## Week three of AN597. [Modules 6](https://fuzzyatelin.github.io/bioanth-stats/module-06/module-06.html) and [Module 7](https://fuzzyatelin.github.io/bioanth-stats/module-07/module-07.html).

# The premise for this homework is: 
> Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

## Question 1: What is the probability that she will hear more than 8 calls during any given session?
### Quotation explaining how you are conceptualizing and making sense of the question
``` {r}
x <- 5*8
x
```

```{r}

```

