---
title: "cavega_OriginalHomeworkCode_02"
author: "C. Vega"
date: "9/16/2019"
output: html_document
---

# This is the code for [Homework 2](https://fuzzyatelin.github.io/bioanth-stats/homework-02.html)

# The premise for this homework is: 
> Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

## Question 1: What is the probability that she will hear more than 8 calls during any given session?
### (Quotation explaining how you are conceptualizing and making sense of the question)
``` {r}
x <- 5*8
x
```
## Question 2: What is the probability that she will hear no calls in a session?
### Explanation of thinking for Question 2
```{r}

```

## Question 3: What is the probability that she will hear exactly 3 calls in a session?
```{r}

```

## Question 4: Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.
```{r}

```

## Question 5: Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).
```{r}

```

## Question 6: Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?
```{r}

```

***

# Peer Commentary (5 Challenges)

***

1. 
2. 
3. 
4. 
5. 