---
title: "cavega_PeerCommentary_feiyaw_02"
author: "C. Vega"
date: "9/16/2019"
output: html_document
---

# This is the code for [Homework 2](https://fuzzyatelin.github.io/bioanth-stats/homework-02.html)

# The premise for this homework is: 
> Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

## Question 1: What is the probability that she will hear more than 8 calls during any given session?
### For this I am using the ppois function, where lambda is the average, and the variable is the first number in the parentheses, i will use the call >lower.tail=FALSE to look at the probability of getting a number greater than 8
### My answer shows that there is a 96.3% chance that there will be more than 8 calls in a two-hour window.
``` {r}
ppois(8, lambda = 15, lower.tail = FALSE)
```
## Question 2: What is the probability that she will hear no calls in a session?
### Here I am using ppois again to test the probability that she will not hear any calls. I am not including >lower.tails because it is automatically set to TRUE in this function
### My answers shows that there is a 0.00003059% chance of hearing 0 calls in a two hour session. 
```{r}
ppois(0, lambda = 15)
```

## Question 3: What is the probability that she will hear exactly 3 calls in a session?
### The probability of hearing exactly 3 calls is 0.017% 
```{r}
dpois(x = 3, lambda = 15)
```

## Question 4: Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.
### I will be using code from Module 8 to make a plot of the probability of values from 0 to 30
### Originally tried this but it is wrong:
    > barplot(ppois(x, lambda=l), 
          ylim=0:1, space=0, names.arg = x, xlab = "Number of Calls", 
          ylab= "Probability", main="Question 4: Poisson Mass Function for Titi Calls")
          
```{r}
x <- 0:30
l <- 15

barplot(dpois(x=x,lambda=l),  names.arg=x,space=0,xlab="x",ylab="Probability",main="Question 4: Probability Mass Function for Titi Calls")
```

## Question 5: Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).
### I am using rnorm to simulate 104 observations, with an expected mean of 15 within the interval 0:30. I took the mean of this result (v) to see if it made sense. (It changes every time because it is a new random set of numbers every time.)

```{r}
v <- rnorm(104, 15)
mean(v)
```

## Question 6: Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?
### I tried plotting this with the limits from 0:30 as the question asks, but this does not seem like the proper result. 
```{r}
v <- rnorm(104, 15,)

hist(v, xlim = c(0,30), xlab = "Number of Calls", ylab= "Frequency", main = "Question 6: Histogram of Simulated Calls")
```

***
# Peer Commentary by Feiya Wang
you did a great job on first 4 question. However, for the uqestion 5 and 6, it have some problem. First, the function rnom() is sued for the normal distribution, we cannot use it for this question since it is a Poisson distribution. you need to change this function. Secondly, question 5 need 104 random value from those distribution, but you only provide 1 values  on your question 5. I suggested that you delete the function mean(v) so we cna get 104 values. Thirdly, the question 5 and 6 ask for the same set of numbers. if you use two random question, you will get different results. I suggest that for question5, and 6, you use the same R shell so that the variable can be continue use whne you graph them. Also, you are getting a results of a narrow graph is because you use the normal distribution function instead of Poisson distribution. The normal distibution in your function assume that standard deviation is actually 1. therefore, as the first suggestion, you may want to change your function for Poisson distribution. 


***
***

#5 Challenges

***

## 1. I am very unfamiliar with probability, so when I came up with an answer for the first few questions, I did not know what a "reasonable" answer would be. 
## 2. It took me a lot of time to figure out which code to use to make the graphs
## 3. Even with the amount of time spent on figuring out the graphs (Questions 4 and 6), I am still not sure that they are correct.
## 4. I do not think that I correctly bootstrapped/ simulated the results for Questions 5 and 6.
## 5. It took me a long time to get through Module 8, and I still wouldn't be able to identify when to use each type of distibution plot.