---
title: "cavega_PeerCommentary_feiyaw_02"
author: "C. Vega"
date: "9/16/2019"
output: html_document
---

# This is the code for [Homework 2](https://fuzzyatelin.github.io/bioanth-stats/homework-02.html)

# The premise for this homework is: 
> Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

## Question 1: What is the probability that she will hear more than 8 calls during any given session?
### For this I am using the ppois function, where lambda is the average, and the variable is the first number in the parentheses, i will use the call >lower.tail=FALSE to look at the probability of getting a number greater than 8
### My answer shows that there is a 96.3% chance that there will be more than 8 calls in a two-hour window.
``` {r}
ppois(8, lambda = 15, lower.tail = FALSE)
```
## Question 2: What is the probability that she will hear no calls in a session?
### Here I am using ppois again to test the probability that she will not hear any calls. I am not including >lower.tails because it is automatically set to TRUE in this function
### My answers shows that there is a 0.00003059% chance of hearing 0 calls in a two hour session. 
```{r}
ppois(0, lambda = 15)
```

## Question 3: What is the probability that she will hear exactly 3 calls in a session?
### The probability of hearing exactly 3 calls is 0.017% 
```{r}
dpois(x = 3, lambda = 15)
```

## Question 4: Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.
### I will be using code from Module 8 to make a plot of the probability of values from 0 to 30
          
```{r}
x <- 0:30
l <- 15

barplot(dpois(x=x,lambda=l),  names.arg=x,space=0,xlab="x",ylab="Probability",main="Question 4: Probability Mass Function for Titi Calls")
```

## Question 5: Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).
### I have changed from using rnorm to rpois (because this is not a normal distribution and necessitates using Poisson). This way, I am getting 104 random results and then applying them to question 6.

```{r}
v <- rpois(104, lambda= 15)
v
```

## Question 6: Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?
### I changed this with the new "v" value and the graph makes a lot more sense. Now it looks to have a more even distribution that you would expect with an average of 15. 
```{r}

hist(v, xlim = c(0,30), xlab = "Number of Calls", ylab= "Frequency", main = "Question 6: Histogram of Simulated Calls")
```


***

Final Commentary: My peer commenter really helped identify where I was going wrong. I had all the right values yet used the wrong distribution function. Although this homework tells which function to use, I would like to know how to distinguish between functions in the future when the answer is more ambiguous. I would also like a better explanation of when to use rpois, dpois, and ppois.

***



